\section{Results}
\label{sec:results}

The statistical only significance based on BDT discriminant is shown in Table \ref{tab:tthML_significance}, \ref{tab:xTFW_significance}.

\begin{table}
\caption{The statistical only significance in leptonic channels based on BDT discriminant.}
\label{tab:tthML_significance}
\input{\FCNCTables/tthML/showFake/faketau/postfit/NOMINAL_SROnly/significance_chart}
\end{table}

\begin{table}
\caption{The statistical only significance in hadronic channels based on BDT discriminant.}
\label{tab:xTFW_significance}
\input{\FCNCTables/xTFW/showFake/NOMINAL/significance_chart}
\end{table}

The significance of any small observed excess in data is evaluated by quoting the $p$-values to quantify the level of consistency of the data with the $\mathcal{B}=0$ hypothesis. The asymptotic approximation in \cite{CCGV} is used. The test statistic used for the exclusion limits derivation is the $\tilde{q}_\mu$ test statistic
and for the $p$-values the $q_{0}$ test statistic\footnote{The definition of the test statistics used in this search is the following:
\[ \tilde q_\mu = \left\{
  \begin{array}{l l}
    -2 \ln (\mathcal{L}(\mu,\hat{\hat{\theta}})/\mathcal{L}(0,\hat{\hat\theta})) & \quad \text{if $\hat\mu < 0$}\\
    -2 \ln (\mathcal{L}(\mu,\hat{\hat{\theta}})/\mathcal{L}(\hat \mu,\hat\theta)) & \quad \text{if $0 \leq \hat\mu \leq \mu$}\\
    0 & \quad \text{if $\hat\mu > \mu$}
  \end{array} \right.\]
and
\[ q_0 = \left\{
  \begin{array}{l l}
    -2 \ln (\mathcal{L}(0,\hat{\hat{\theta}})/\mathcal{L}(\hat\mu,\hat\theta)) &\quad \text{if $\hat\mu \geq 0$}\\
    0 & \quad \text{if $\hat\mu <0$}
  \end{array} \right.\]
where $\mathcal L(\mu,\theta)$ denotes the binned likelihood function, $\mu$ is the parameter of interest (i.e.
the signal strength parameter), and $\theta$ denotes the nuisance parameters. The pair $(\hat\mu, \hat\theta)$
corresponds to the global maximum of the likelihood, whereas $(x, \hat{\hat\theta})$ corresponds to a conditional
maximum in which $\mu$ is fixed to a given value $x$.
}
\cite{CCGV}.

The $95\%$ CL upper limits on $tqH$ interaction with $\mathcal{B}(t\to Hq)=0.1\%$ as reference are given in Table~\ref{tab:tab_tthML_limit} and \ref{tab:tab_xTFW_limit} (Table \ref{tab:tab_tthML_limit_statsOnly} and \ref{tab:tab_xTFW_limit_fakeOnly} are limits with only fake estimation method and statistical uncertainties included.) for leptonic and hadronic channels respectively. The expected limits combining all channels are given in Table \ref{tab:limit} (Table~\ref{tab:limit_statsOnly} are limits with only fake estimation method and statistical uncertainties included.) and Figure \ref{fig:combined_limit}. The sensitivity is significantly improved compared to the published results~\cite{fcncgmgm,fcncml,fcnctautau}. 

Upper limits on the branching ratios $\mathcal{B}(t\to Hq)$ ($q=u,c$) can be translated into upper limits on the dimension-6 (D6) operator wilson coefficients appearing in the effecitive field theory Lagrangian for $tqH$ interaction in Eq.~\ref{eq:eq01}.
The branching ratio $\mathcal{B}(t\to Hq)$ is estimated as the ratio of its partial width to the SM $t \to Wb$ partial width including next-to-leading-order QCD corrections and the coefficients can be extracted as $C_{q\phi} = \sqrt{1946.6~\mathcal{B}(t\to qH)}$.
The $C_{q\phi}$ coefficient corresponds to the sum in quadrature of the cofficients relative to the two possible chirality combinations of the quark fields,
$C_{q\phi} =\sqrt{(C^{i3}_{u\phi})^2 + (C^{3i}_{u\phi})^2}$~\cite{fcnc_production_theory}. The observed (expected) upper limits on the D6 Wilson coefficients from the combination of the searches are $C_{c\phi}<1.38\,(0.97)$ and $C_{u\phi}<1.18\,(0.83)$.

A similar set of results can be obtained by simultaneously varying both branching ratios in the likelihood function. Figure~\ref{fig:combined_2D_limit}(left) shows the 95\% CL upper limits on the branching ratios in the $\mathcal{B}(t\rightarrow Hu)$
versus $\mathcal{B}(t\rightarrow Hc)$ plane. The corresponding upper limits on the D6 Wilson coefficients couplings in the $C_{u\phi}$ versus $C_{c\phi}$ plane are shown in Figure~\ref{fig:combined_2D_limit}(right).
%The values of the branching ratio limits obtained in the two-dimensional scan on the x- and y-axes is in coincidence with that presented in Table \ref{tab:limit}.

The search for the FCNC decay $t\to Hq, H\to\tau\tau$ with the ATLAS detector at the LHC using 13~\TeV{} data was presented in this note. The best-fit values for $\mathcal{B}(t\to Hc)$ and $\mathcal{B}(t\to Hu)$ are found to be $0.037\pm0.018\%$ and $0.051\pm0.025\%$ respectively, based on 139 $\ifb$ of data collected from 2015 to 2018. The observed (expected) $95\%$ CL upper limits on $\mathcal{B}(t\to Hc)$ and $\mathcal{B}(t\to Hu)$ are found to be $0.099\%$ ($0.048^{+0.021}_{-0.013}\%$) and $0.072\%$ ($0.035^{+0.016}_{-0.010}\%$), respectively.

%The best asimov fit values with S+B hypothesis are given in Table~\ref{tab:tab_best_fit}.
%Note that the current results only consists of fake estimation NPs.

\begin{table}[htb]
\caption{ The expected $95\%$ CL exclusion upper limits on signal ( $\mu=1\to~\mathcal{B}(t\to Hq)=0.1\%$ ) with the Asimov (B-only) in the leptonic channels, only statistical and fake estimation uncertainties included.}
\input{\FCNCTables/tthML/limits_statsOnly}
\label{tab:tab_tthML_limit_statsOnly}
\end{table}

\begin{table}[htb]
\caption{ The combined $95\%$ CL exclusion upper limits(top) and significances(bottom) on signal with Asimov data and ublinded data(values in parentheses are expected) in the leptonic channels, all uncertainties included.}
\input{\FCNCTables/tthML/limits}
\label{tab:tab_tthML_limit}
\end{table}

\begin{table}[htb]
\caption{ The expected $95\%$ CL exclusion upper limits on signal ( $\mu=1\to~\mathcal{B}(t\to Hq)=0.1\%$ ) with the Asimov (B-only) in the hadronic channels, only statistical and fake estimation uncertainties included.}
\input{\FCNCTables/xTFW/limits_fakeOnly}
\label{tab:tab_xTFW_limit_fakeOnly}
\end{table}

\begin{table}[htb]
\caption{ The combined $95\%$ CL exclusion upper limits(top) and significances(bottom) on signal with Asimov data and ublinded data(values in parentheses are expected) in the hadronic channels, all uncertainties included.}
\input{\FCNCTables/xTFW/limits}
\label{tab:tab_xTFW_limit}
\end{table}

\begin{table}[htb]
\caption{ The combined expected $95\%$ CL exclusion upper limits on signal ( $\mu=1\to\mathcal{B}(t\to Hq)=0.1\%$ ) with the Asimov (B-only), only statistical and fake estimation uncertainties included.}
\input{\FCNCTables/limits_statsOnly}
\label{tab:limit_statsOnly}
\end{table}

\begin{table}[htb]
\caption{ The combined $95\%$ CL exclusion upper limits(top) and significances(bottom) on signal with Asimov data and ublinded data(values in parentheses are expected), all uncertainties included.}
\input{\FCNCTables/limits}
\label{tab:limit}
\end{table}

\input{\FCNCFigures/unblinded/combined_limit}

