\section{To do list}

Continue to improve the documentation and preparing the paper draft.

\section{On going studies}

Preparing the analysis (pre)-approval.

\section{Change log}

\subsection{From V1 to V2}

Leptonic channels:  80fb-1 $\to$ 140fb-1

BDT tau ID $\to$ RNN tau ID

Updates to PFlow jets with DL1r b-tagging.

Optimised event seletion.

Changed fake estimation method.

Added signal regions $l\tau$ 1j and $l\tau$ 2j.

\subsection{From V2 to V3}

Added to do list and change log.

Added Analysis outline section and moved signal region definition here.

Added yield tables for CRs.

Added plots for the variables defined.

Added closure test for ABCD method.

BDT optimisation.

\subsection{From V3 to V3.1}

Made the note more readable by introducing new names for SR and CR.

...
\subsection{From V3.1 to V4.0}

Updated with full systematics.

Improved figures, clarified a few statements.

Bug fix:

1. Add the missing Double fake contribution in $t_l\tauhad\tauhad$ regioninto the fit.

2. Require b-veto for the subleading tau in $t_l\tauhad\tauhad$ region

\subsection{From V4.0 to V5.0}

Added PS and ME systematics for ttbar sample.

Using recommended blinding strategy.

\subsection{From V5.0 to V5.1}

Decorrelate PS and ME systematics between signal and ttbar.

Use AFII PowhegPythia* ttbar sample and AFII PowhegHerwig7 sample for PS uncertainty.

Added pruning plots.

Added appendices for:

1. Systematics variation comparison plots.

2. Pull and correlation matrix for the fits with different signal.

\subsection{From V5.1 to V5.2}

1. Use AFII 410470 vs AFII PowhegHerwig7.0 (410557/410558) for PS uncertainty.

2. Decorrelated the PS uncertainty between signal and ttbar background.

3. Added appendice F. the decorrelation studies between different signal regions to understand the source of over-constraining.

4. Fixed reference format.

\subsection{From V5.2 to V5.3}

1. Changed the default value of B(t$\rightarrow$Hq) from 0.2\% to 0.1\% to be consistent with the blind strategies.

2. Re-trained the BDT using the Ncuts and Ntree obtained from the optimization studies made based on independent Herwig7 samples.

3. Added appendice~\ref{sec:kine} for the comparison of the sensitivity using different di-tau kinematic fits with MMC and a colinear fit without Higgs mass constraint.

4. Added appendice~\ref{sec:CheckPLIV} for checks on the PLIV cut efficiencies for the e/mu from the tau decay using $Z\rightarrow\tau\tau\rightarrow e\mu$ events.

5. Moved some yields tables into appendice~\ref{sec:Yield_Table}.

6. Improved the table and figure captions to be more readable. 


\subsection{From V5.3 to V5.4}

1. Minor update to address the remaining EB comments

2. Added btag systematic checks in Appendix D. 

\subsection{From V5.4 to V5.5}

1. Checked HVV contamination to the lephad channels in Appendix J.

2. Added extra +-2\% uncertainty for the PLIV cut efficiency for the light lepton from the tau decay in the fits for the lephad channels.

3. Added some details about the TMVA training on the correlation between input variables and over-training checks in Appendix K.

4. Checked NLL scan to understand the fits for some of systematic dependents.

5. Change the correlation theshold form 20\% to 1\% to see the correlation between mu and high ranking B\_tag systematics.

\subsection{From V5.5 to V5.6}

1. Added ztautau and rare sample theoretical uncertainties .

2. Added PS and PS71 uncertainty comparison.

3. Added hdamp and ME comparasion.

4. Fixed some typos in the MC sample descriptions.

\subsection{From V5.6 to V5.7}

1. Checked the BONLY fits in $t_h\tlhad$-3j and $t_l\tauhad$-1j signal regions with $BDT<0.2$ and the impact on the limits is estimated by
rescaling the corresponding background from the fit.

2. The impact of the gluon-quark fraction is studied by comparing the defualt value of $(50\pm50)$\% and the actual one measured from MC.

3. Fixed some typos and added some text to make the note more clear. 

\subsection{From V5.7 to V5.8}

1. The distributions of the fake tau factor(FF) are shown in Appendix D.

2. Addressed the comments from the unblinded approval. 

\subsection{From V5.8 to V5.9}
1. Addressed the comments from the closure meeting, the new added contents are in appendixD.
2. Move the Asimov results to appendixE, add the unblined results in the body of the notes.


